Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

\begin{theorem} \label{thm:main-alg}
    For $k \ge 3$, we can settle $k$-SJ with a comparison-based algorithm in $O( c^{k-1} (k!)^3 \cdot (n \log n + k \cdot \out))$ time.
    %and $O(k \cdot n + \out)$ space, where $c > 1$ is a positive constant.
\end{theorem}

@@

\def\vgap{\vspace{1mm}}
\def\extraspacing{\vspace{1.5mm} \noindent}

>>>>

\begin{theorem} \label{thm:main-alg}
    For $k \ge 3$, we can settle $k$-SJ with a comparison-based algorithm in $O( c^k \cdot (k!)^3 \cdot (n \log n + k \cdot \out))$ time, where $c > 1$ is a positive constant.
    %and $O(k \cdot n + \out)$ space,
\end{theorem}

@@

\def\vgap{\vspace{0.5mm}}
\def\extraspacing{\vspace{1.5mm} \noindent}
